### 2021-03-22 Chapter-1/Chapter-1.tex
Updates from Overleaf

We try to address the above problem from the following aspects.
\begin{enumerate}
\item 
\item We propose a novel method to quantify information 
leakage precisely from a single trace attack. We quantify the number of bits that can leak during a real execution and define the amount of leaked information as the cardinality of possible secrets based on an attacker's observation. Before an attack, an adversary has a large but finite input space. Whenever the adversary observes a leakage site, they can eliminate some impossible inputs and reduce the input space's size. In an extreme case, if the input space's size reduces to one, an adversary has determined the input, which means all secret information (e.g., the entire secret key) is
leaked. By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely.
We use symbolic execution to generate constraints to model the relation 
between the original sensitive input and an attacker's observations. 
Symbolic execution provides fine-grained information, but it is expensive
to compute. Therefore, prior symbolic
execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only
small programs or applies domain knowledge~\cite{203878} to simplify the analysis. We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work for real-world crypto-systems.

@@

\section{Address-based Side-channel}
\subsection{Attack}
Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim. As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

Cache channels rely on the time difference between cache misses and cache hits. A cache channel works when the victim program and the attacker's program shares some sized chunks like cache lines or cache sets. Recent studies shows that an attacker can even observe the address access at a finer granularity (e.g., CacheBleed). Page-level side-channels allow attackers observe the memory access at the granularity of memory pages.

In this dissertation, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs). To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.

When we examine those side-channel attacks, many of them stem from the two code patterns, \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
\begin{figure}[h]
\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
int secret[32];
...
while(i>0){
    r = (r * r) % n;
    if(secret[--i] == 1)
        r = (r * x) % n;   
}
\end{lstlisting}
\caption{Secret-dependent control-flow transfers}
\label{fig:secret:cf}
\end{figure}

Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes. Figure~\ref{fig:secret:cf} shows an example. Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6. As attackers, they can retrieve some information based on the execution control-flow.

\begin{figure}[h]
\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
static char FSb[256] = {...}
... 
uint32_t a = *RK++ ^ \ 
(FSb[(secret)) ^
(FSb[(secret >> 8)] << 8 ) ^
(FSb[(secret >>16)] << 16 ) ^
(FSb[(secret >>24)] << 24 );
...
\end{lstlisting}
\caption{Secret-dependent data accesses}
\label{fig:secret:da}
\end{figure}

Secret-dependent data accesses happen when the value of the secret can affect which memory cell the code reads or writes. Figure~\ref{fig:secret:da} shows an example. \textsf{FSb} is an array. Depending on the value of \textsf{secret}, the code may read or write different items in the array.

\subsection{Defense}

Both hardware~\cite{Page2005PartitionedCA,
Wang:2007:NCD:1250662.1250723,Zhang:2015:HDL:2775054.2694372,Li:2014:SLH:2541940.2541947,
236344, 236334} and software~\cite{shih2017t,Coppens:2009:PMT:1607723.1608124,
brickell2006software,crane2015thwarting, 197207} side-channels mitigation techniques have
been proposed recently. Hardware countermeasures, including partitioning hardware resources~\cite{Page2005PartitionedCA}, randomizing cache
accesses~\cite{Wang:2007:NCD:1250662.1250723, 236344}, and designing new
architecture~\cite{tiwari2011crafting}, require changes to complex processors and are complex to adopt.

>>>>

We try to address the above problem from the following aspects.
\begin{enumerate}
\item \textbf{Detection.} We propose a fast and precise side-channel detection method. Different from previous trace comparison based methods, our method has fewer false positives and false negatives. Compared with methods based on symbolic execution and abstract interpretation, our methods can work on real-world cryptography libraries. Symbolic execution provides fine-grained information, but it is expensive to compute. Therefore, prior symbolic
execution work~\cite{203878,236338,Brotzman19Casym} either analyzes only
small programs or applies domain knowledge~\cite{203878} to simplify the analysis. We examine the bottleneck of the trace-oriented symbolic execution and optimize it to work for real-world crypto-systems.
\item \textbf{Quantification.} We propose methods to quantify information 
leakage precisely from a single trace attack. We quantify the number of bits that can leak during a real execution and define the amount of leaked information as the cardinality of possible secrets based on an attacker's observation. Before an attack, an adversary has a large but finite input space. Whenever the adversary observes a leakage site, they can eliminate some impossible inputs and reduce the input space's size. In an extreme case, if the input space's size reduces to one, an adversary has determined the input, which means all secret information (e.g., the entire secret key) is
leaked. By counting the number of inputs~\cite{10.1007/11499107_24}, we can quantify the information leakage precisely. We use symbolic execution to generate constraints to model the relation 
between the original sensitive input and an attacker's observations.

@@

### 2021-03-22 Chapter-2/Chapter-2.tex
Updates from Overleaf

>>>>

Address-based side-channel attacks happen when a program has different behaviors when it accesses different memory addresses. Most systems allows the attacker to shares some hardware resources (e.g., CPU Cache, TLB, and DRAM) with the victim. As a result, while the root reason of the attack is the same, there are various approaches that can exploit the attack at different granularities.

Cache channels rely on the time difference between cache misses and cache hits. A cache channel works when the victim program and the attacker's program shares some sized chunks like cache lines or cache sets. Recent studies shows that an attacker can even observe the address access at a finer granularity (e.g., CacheBleed). Page-level side-channels allow attackers observe the memory access at the granularity of memory pages.

In this dissertation, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs). To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.

When we examine those side-channel attacks, many of them stem from the two code patterns, \emph{secret-dependent control-flow transfers} and \emph{secret-dependent data accesses}.
\begin{figure}[h]
\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
int secret[32];
...
while(i>0){
    r = (r * r) % n;
    if(secret[--i] == 1)
        r = (r * x) % n;   
}
\end{lstlisting}
\caption{Secret-dependent control-flow transfers}
\label{fig:secret:cf}
\end{figure}

Secret-dependent control-flow transfers happen when the value of secret can affect which branch the code executes. Figure~\ref{fig:secret:cf} shows an example. Depending on the value of \textsf{secret}, the code may or may not execute the code at line 6. As attackers, they can retrieve some information based on the execution control-flow.

\begin{figure}[h]
\begin{lstlisting}[xleftmargin=.32\textwidth, xrightmargin=.32\textwidth]
static char FSb[256] = {...}
... 
uint32_t a = *RK++ ^ \ 
(FSb[(secret)) ^
(FSb[(secret >> 8)] << 8 ) ^
(FSb[(secret >>16)] << 16 ) ^
(FSb[(secret >>24)] << 24 );
...
\end{lstlisting}
\caption{Secret-dependent data accesses}
\label{fig:secret:da}
\end{figure}

Secret-dependent data accesses happen when the value of the secret can affect which memory cell the code reads or writes. Figure~\ref{fig:secret:da} shows an example. \textsf{FSb} is an array. Depending on the value of \textsf{secret}, the code may read or write different items in the array.
